Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-12-31 manuscript/main.tex
Update TB funding
Acknowledge Bing, simplify funding text

We thank Jesse Bloom, Erick Matsen, Harmit Malik, Sidney Bell, Alli Black, Lola Arakaki, and members of the Bedford lab for useful advice and discussions.
JH is a Graduate Research Fellow and is supported by the National Institute Of Allergy And Infectious Diseases under NIH F31AI140714.
TB is a Pew Biomedical Scholar and is supported by NIH R35 GM119774-01.
\jhc{Add RN support here.}

>>>>

We thank Jesse Bloom, Erick Matsen, Bing Brunton, Harmit Malik, Sidney Bell, Alli Black, Lola Arakaki, and members of the Bedford lab for useful advice and discussions.
JH is a Graduate Research Fellow and is supported by the NIH grant NIAID F31AI140714.
TB is a Pew Biomedical Scholar and is supported by NIH grants NIGMS R35 GM119774-01, NIAID U19 AI117891-01 and NIAID R01 AI127893-01.
\jhc{Add RN support here.}
